Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration

### 2018-06-28 chapters/introduction/introduction.tex
complete draft

Study of geo-localization has a long history.

\section{Our Approach}
My thesis focuses on the image understanding with camera geometry.
There are two directions we will address: 1) How to estimate camera
geometry from images; 2) How can we use camera geometry to improve the
current methods for image semantic extracting. For the first direction,
we explore both the traditional method and deep learning approaches on
different geometric calibration parameters. For the second direction,
we will exploit the image geometric location to help extract
semantically meaningful informations from images.

  \item \textbf{Camera Geometry Detection:} 
  We investigate different methods to detect camera geometry from the
  input images. We first explore a sampling approach to find the
  complete camera calibration parameters that fit the observation of
  objects (input image) best. In our next work, we use a deep neural
  network to learn to detect horizon line and vanishing points. These
  two approaches provides information for the next stage of our
  research.

  \item \textbf{Camera Geometry for Image Understanding:}
  We explore the potentials of camera geometry for image understanding.
  Current machine learning methods address problems that involves mostly
  the ground imagery. 
  Studies around overhead images are relatively less thus much fewer
  annotated data exists in public. With the camera geometric
  information, we can pair the ground imagery with overhead imagery to
  form cross-view pairs. Our algorithm explore how to transfer the
  learned knowledge from a network designed for ground level image
  semantic segmentation to a new network designed for overhead imagery
  semantic segmentation use these cross-view pairs.
  Furthermore, we also explore the potential of the camera geometry as
  weak annotation in supervised learning. Our algorithm shows that by
  directly learning to predict camera locations, the network networks
  are able to extract high-level geo-temporal features.

@@

  \item \textbf{\chapref{crosstransf} -
  Cross-view Domain Adaptation:} \newline \newline
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. \newline

  \item \textbf{\chapref{whenwhere} -
  Extract High-Level Feature by Learning When and Where:} \newline \newline
  One of the key to the success of machine learning approaches are the
  large quantity of annotated data. However, fully annotated imagery
  only consists of a tiny part of the image resources available online.
  The idea is to exploit other meta-info that are automatically
  recorded/captured by devices to train the ML models.  We demonstrate
  that the camera geometry can be used as weak ground truth for
  supervision problem. By learning the capture time and the geolocation
  of the images, our network is able capture the geo-temporal related
  high-level features. \newline

>>>>

Study of geo-localization has a long history. \todo{citations}. We
seek to geo-localize images with temporal information. The system
estimate the geographic location of the camera in the form of discrete
probabilities over bins. This application works in rough scale. We
also design another algorithm that can do finer scale localization
based on the rough location input. In that work, we train a network to
transfer the semantic segmentation masks from the top-view perspective
to the ground view perspective. In order to train the network, we have
to construct the image pairs called cross-view image pairs.

Overhead imagery plays an import role in the cross-view learning area.
To construct a cross view image pair, we need to know the geographic
location (sometimes also with the geographic orientation).
\todo{copy from scott} Efforts have been made to
automate overhead image analysis. As early as
1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.

Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options. With
the geographic information of the ground image, we are able to
download the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.

Our algorithm takes advantage of cross-view pairs, to train a deep
neural network that can semantically segment the overhead image and
then transfer the segmentation mask to the ground view. To finer
geo-orient and localize the image, we can match the ground
segmentation mask with the mask generated from overhead image at
location $l$.

Another contribution of our work is that along the training for
networks that do geo-calibration, we are able to learn to extract
high-level features from the networks along side.

\section{Our Approach}
Our thesis focus on constructing a probabilistic model for camera
geo-calibration. To do that, we first develop an general architecture
for geo-calibration with different constraint functions. We then seek
to conquer constraints in subset of calibration parameters.

\begin{itemize}[noitemsep]
  \item \textbf{General Architecture for Geo-Calibration:}
  We designed a graphic model to estimate the probability over
  geo-calibration parameter space.

  \item \textbf{Constraints for Subset Parameters:}
  Divide and conquer the problems.

@@

  \item \textbf{\chapref{whenwhere} -
  Learn Where with When:} \newline \newline
  One of the key to the success of machine learning approaches are the
  large quantity of annotated data. However, fully annotated imagery
  only consists of a tiny part of the image resources available online.
  The idea is to exploit other meta-info that are automatically
  recorded/captured by devices to train the ML models.  We demonstrate
  that the camera geometry can be used as weak ground truth for
  supervision problem. By learning the capture time and the geolocation
  of the images, our network is able capture the geo-temporal related
  high-level features. \newline

  \item \textbf{\chapref{crosstransf} -
  Finer Localization by Matching the Overhead Images:} \newline \newline
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. \newline

### 2018-06-28 chapters/introduction/junk.tex
complete draft

>>>>

My thesis focuses on the image understanding with camera geometry.
There are two directions we will address: 1) How to estimate camera
geometry from images; 2) How can we use camera geometry to improve the
current methods for image semantic extracting. For the first direction,
we explore both the traditional method and deep learning approaches on
different geometric calibration parameters. For the second direction,
we will exploit the image geometric location to help extract
semantically meaningful informations from images.

\begin{itemize}[noitemsep]

  \item \textbf{Camera Geometry Detection:} 
  We investigate different methods to detect camera geometry from the
  input images. We first explore a sampling approach to find the
  complete camera calibration parameters that fit the observation of
  objects (input image) best. In our next work, we use a deep neural
  network to learn to detect horizon line and vanishing points. These
  two approaches provides information for the next stage of our
  research.

  \item \textbf{Camera Geometry for Image Understanding:}
  We explore the potentials of camera geometry for image understanding.
  Current machine learning methods address problems that involves mostly
  the ground imagery. 
  Studies around overhead images are relatively less thus much fewer
  annotated data exists in public. With the camera geometric
  information, we can pair the ground imagery with overhead imagery to
  form cross-view pairs. Our algorithm explore how to transfer the
  learned knowledge from a network designed for ground level image
  semantic segmentation to a new network designed for overhead imagery
  semantic segmentation use these cross-view pairs.
  Furthermore, we also explore the potential of the camera geometry as
  weak annotation in supervised learning. Our algorithm shows that by
  directly learning to predict camera locations, the network networks
  are able to extract high-level geo-temporal features.
\end{itemize}
